---
title: "Foundation"
output: github_document
---

Working on FPO data, as published in the [UK Foundation Programme](http://www.foundationprogramme.nhs.uk/content/reports), "Recruitment Stats and Facts, Interim Report April 2017".

To do this I've used a new package - [Tabulizer.](https://github.com/ropensci/tabulizer)

This was probably one of the hardest set-ups I've had to do.
After downloading several different versions of Java, I had some luck with this [set-up guide.](https://zhiyzuo.github.io/installation-rJava/)


I would say it's been worth the effort however.

# Load in Libraries
```{r, message=FALSE, warning=FALSE}
library(tabulizer)
library(tidyverse)
```

# Load in Tables
```{r}
pdf <- "2017_Recruitment_Stats_and_Facts.pdf"
data <- extract_tables(pdf, output = "data.frame", header = TRUE)
```

# Index
```{r, echo=FALSE}
data[[2]] %>%
  head
```

# Table: 1.2: Local AFP Applications and FP Preferences by Medical School
```{r, warning=FALSE}
example1 <- data[[4]] %>%
  filter(X == "University of Glasgow") %>%
  select(-X) %>%
  rename("Number Applied to Local AUoA" = Number) %>%
  rename("% Applied to Local AUoA" = X.1) %>%
  rename("Number Preferenced Home UoA" = Number.1) %>%
  rename("% Preferenced Home UoA" = X.) %>%
  print()
```

# Table 2.7: Local Applications by Medical School
```{r, echo=FALSE}
example2 <- data[[10]] %>%
  filter(X == "University of Glasgow") %>%
  select(-X) %>%
  rename("Number Applied" = X.1) %>%
  rename("Number who Preferenced Home UoA" = Number.who) %>%
  rename("% who Preferenced Home UoA" = X..who) %>%
  print()
```

# Table 2.8: FP Programme Preferences
```{r, echo=FALSE}
example3 <- data[[11]] %>%
  filter(X == "Scotland") %>%
  select(-c(X, X.1)) %>%
  rename("Number of Applicants who Preferenced UoA First" = 
Number.of) %>%
  rename("Number of Applicants who Preferenced UoA Second" = Number.of.1) %>%
  rename("Number of Applicants who Preferenced UoA Third" = Number.of.2) %>%
  print()
```

# Table 2.9: FP Total Scores by Medical School
```{r, echo=FALSE}
example4 <- data[[12]] %>%
  filter(X == "University of Glasgow") %>%
  select(-X) %>%
  rename("FP 2016: SJT + EPM (deciles) (Max. score: 100)" = FP.2016..SJT...EPM) %>%
  rename("FP 2017: SJT + EPM (deciles) (Max. score: 100)" = FP.2017..SJT...EPM) %>%
  print()

#c("Ave", "Std. Dev.", "Max", "Min")
```

# Table 2.10: Application Results by Medical School
```{r, echo=FALSE}
example5 <- data[[13]] %>%
  filter(X == "University of Glasgow") %>%
  select(-X) %>%
  rename("Number Applied" = X.1) %>%
  rename("Number Applied to FP (excl. AFP Offers)" = X.2) %>%
  rename("Percentage of Total Applicants in FP Allocation" = Percentage) %>%
  rename("Allocated to Primary List" = X.3) %>%
  rename("Percentage Allocated to Primary List" = X.4) %>%
  print()
```

# Table 2.11: Preference Allocation Results Information by Medical School
```{r, echo=FALSE}
example6 <- data[[14]] %>%
  filter(X == "University of Glasgow") %>%
  select(-X) %>%
  rename("Number Allocated to First Preference" = X.1) %>%
  rename("% Allocated to First Preference" = X.2) %>%
  rename("Number Allocated to Top 5 Preference" = X.3) %>%
  rename("Percentage Allocated to Top 5 Preference" = X.4) %>%
  rename("Percentage Allocated Lower than Top 5 Preference" = Percentage) %>%
  print()
```

# Table 2.12: FP Application Results by Foundation School
```{r, echo=FALSE}
example7 <- data[[15]] %>%
  filter(X == "Scotland") %>%
  select(-c(X, X.5)) %>%
  rename("Places" = X.1) %>%
  rename("1st pref apps" = X.2) %>%
  rename("% 1st pref apps" = X.3) %>%
  rename("Non-1st pref spaces" = X.4) %>%
  rename("No. allocated via spec circs" = No.) %>%
  rename("% allocated via spec circs" = X.) %>%
  rename("No. allocated to 1st pref" = X.6) %>%
  rename("No. allocated to top 5 prefs" = No..1) %>%
  rename("% allocated to 1st pref" = X.7) %>%
  rename("% allocated to top 5 prefs" = X..1) %>%
  rename("Lowest pref allocated" = X.8) %>%
  rename("Lowest allocated score (excluding s/c)" = Lowest) %>%
  rename("Lowest s/c allocated score" = X.9) %>%
  print()
```

# Table 2.13: SJT scores by medical school (max. score = 50). SJT scores were scaled according to the distribution of EPM decile scores
```{r, echo=FALSE}
example8 <- data[[17]] %>%
  filter(X == "University of Glasgow") %>%
  select(-c(X)) %>%
  rename("FP 2014: SJT Score (only)" = FP.2014..SJT.Score..only.) %>%
  rename("FP 2015: SJT Score (only)" = FP.2015..SJT.Score..only.) %>%
  rename("FP 2016: SJT Score (only)" = FP.2016..SJT.Score..only.) %>%
  rename("FP 2017: SJT Score (only)" = FP.2017..SJT.Score..only..) %>%
  print()

#c("Ave", "SD", "Max", "Min")
```

# Table 3.3: Applications by Medical School
```{r, echo=FALSE}
example8 <- data[[22]] %>%
  filter(X == "University of Glasgow") %>%
  select(-c(X)) %>%
  rename("Number Applied for AFP" = Number) %>%
  rename("Number Offered AFP" = Number.1) %>%
  rename("% Offered AFP" = X.) %>%
  rename("Number Accepted Offer" = Number.2) %>%
  rename("% Accepted Offer" = X..1) %>%
  print()

#c("Ave", "SD", "Max", "Min")
```