---
title: "Fixing 50 Drugs"
output: html_document
---

So I'm planning on fixing 50 Drugs.

Unfortunately, the original data has a lot of formatting issues.

While I could try to programmatically fix some of them, I think the complexity of it vs the size of the dataset means that ultimately it's worth just going through in Excel.

It means the data won't be fixed automatically when I redownload it, but since the 50 drugs resource isn't being actively maintained anymore this seems irrelevant.

```{r}
#Using the fixed version from /anki/index.Rmd
#load drugs.Rda
library(tidyverse)
load("/Users/fergustaylor/Desktop/Repos/Dev/50 Drugs/anki/anki.Rda")
```

```{r, eval = FALSE}
#output as .csv
#totaldataframe%>%
#  write.csv(file = "fix.csv", row.names=FALSE, fileEncoding = #'UTF-8')
```

Edit the csv in Excel.

```{r}
#load .csv
fixeddataframe <- read_csv(file = "fix.csv")
#output as .Rda
save(fixeddataframe, file="fixeddrugs.Rda")
#output as .json
fixeddataframe %>%
  jsonlite::toJSON() %>%
  write(file="fixeddrugs.json")
```
