---
title: "50 Drugs"
---

```{r, warning=FALSE, message=FALSE}
library(rvest)
library(magrittr)
library(stringr)
library(stringi)
library(tidyverse)
library(knitr)
```

#Log in and collect the links
```{r, tidy.opts=TRUE, message=FALSE}
fiftydrugs <- html_session("https://moodle.gla.ac.uk/login/index.php")
```

login <- fiftydrugs %>% 
  html_node("form") %>% 
  html_form() %>%
  set_values(username = "username", password = "password") 
login$url <- "https://moodle.gla.ac.uk/login/index.php"

```{r}
source("dontinclude/script.R")
```

```{r}
data <- fiftydrugs %>% 
  submit_form(login, submit = '<unnamed>') %>%
  jump_to("https://moodle.gla.ac.uk/mod/data/view.php?d=424") %>%
  read_html() %>%
  html_nodes(".defaulttemplate p")
```

#Separate the links
```{r}
links <- ""
for (i in 1:length(data)){
  links[i] <- data[[i]] %>%
    html_children() %>%
    .[2] %>%
    html_attrs() %>%
    as.character()
}

titles <- data %>%
  html_text()

class <- strsplit(titles,":") %>%
  map(1) %>%
  unlist

drug <- strsplit(titles,":") %>%
  map(2) %>%
  unlist

table <- data_frame(class, drug, links)
rm(titles, class, drug, i, links)
```

Follow every link
```{r, tidy.opts=TRUE, warning=FALSE}
linksdata <- ""

datacomplete <- fiftydrugs %>% 
  submit_form(login, submit = '<unnamed>')

#need to fix
for (i in 1:length(table$links)){
linksdata[i] <- datacomplete %>%
    jump_to(table$links[i]) %>%
    read_html() %>%
    html_nodes("form li , #region-main h4")
}
for (i in 1:length(table$links)){
linksdata[[i]] <- datacomplete %>%
    jump_to(table$links[i]) %>%
    read_html() %>%
    html_nodes("form li , #region-main h4")
}
rm(i)
```

```{r}
#function
splitAt <- function(x, pos) split(x, cumsum(seq_along(x) %in% pos))
```

```{r}
listdataframe <- linksdata
#remove unnecessary objects
rm(data, datacomplete, fiftydrugs, login, linksdata)
```

Rewrite linksdata into linksdataframe
```{r}
#searches through the drug page, and selects the relevant parts
for (i in 1:length(table$links)){
subset <- listdataframe[[i]] %>%
rvest::html_attr("class") %>%
  is.na
listdataframe[[i]] <- listdataframe[[i]][subset] 
#looks at the dom type (e.g li or h4)
examplelist <- listdataframe[[i]] %>%
rvest::html_name()
#see what's left
exampletext <- listdataframe[[i]] %>%
  html_text()
#seperate into sections by h4.
listdataframe[[i]] <- splitAt(exampletext, which(examplelist == "h4"))
names(listdataframe[[i]]) <- c("Example(s) of drugs:", "Mechanism of action:", "Indication(s):", "Side effects:", "Important pharmacokinetics / pharmacodynamics:", "Patient information:", "Other information:")
#remove first item of each.
#should swap below for a match against the actual titles
listdataframe[[i]][[1]] <- list(listdataframe[[i]][[1]][-1])
listdataframe[[i]][[2]] <- list(listdataframe[[i]][[2]][-1])
listdataframe[[i]][[3]] <- list(listdataframe[[i]][[3]][-1])
listdataframe[[i]][[4]] <- list(listdataframe[[i]][[4]][-1])
listdataframe[[i]][[5]] <- list(listdataframe[[i]][[5]][-1])
listdataframe[[i]][[6]] <- list(listdataframe[[i]][[6]][-1])
listdataframe[[i]][[7]] <- list(listdataframe[[i]][[7]][-1])
}
rm(i, examplelist, exampletext, subset, splitAt)
```

Split into dataframe
```{r}
dataframe <- data_frame(listdataframe)

clearit <- function(x) {
unlist(x, recursive = FALSE) %>%
.[[1]] %>%
as_data_frame()
}

example <- clearit(dataframe[1,1])
for (i in 2:length(dataframe$listdataframe)){
  example <- rbind(example, clearit(dataframe[i,1]))
}

dataframe <- example
rm(example, i, clearit, listdataframe)
```

https://github.com/rstudio/webinars/blob/master/32-Web-Scraping/navigation-and-authentication.md

Add moodle data to individual drug page data
```{r}
totaldataframe <- cbind(table, dataframe)
head(totaldataframe)
```

Export data
```{r}
totaldataframe %>%
  jsonlite::toJSON() %>%
  write(file="drugs.json")
```

//////////////////
//////////////////
Extra data I might need
```{r}
#html_text(example)[which(examplelist == "h4")]
#should always be 7
#examplelist == "h4"
#which(examplelist == "h4")
```
