
Now scraped, so it can be updated automatically:
```{r, echo=TRUE}
link <- xml2::read_html("http://www.taysideformulary.scot.nhs.uk/chaptersSubDetails.asp?FormularySectionID=5&SubSectionRef=05&SubSectionID=A100&FC=1")
formularydatascraped <- list()

formularydatascraped[[2]] <- link %>% #all titles and drugs, incl non-formulary
  html_nodes(css = ".RowZ100 td , .RowA100 td , .boldDrug") %>%
  html_text %>%
  as.character %>%
  stringr::str_replace_all("\r\n\t  ", replacement = "") %>%
  stringr::str_replace_all("\r\n ", replacement = "") %>%
  str_trim %>%
  unlist %>%
  na_if("")

examplelist2 <- formularydatascraped[[2]] %>%
  lapply(function(x) {str_detect(x, pattern = '[0-9][0-9].[0-9][0-9]')})

formularydatascraped[[3]] <- formularydatascraped[[2]][which(examplelist2 == TRUE)]

formularydatascraped[[2]] <- replace(formularydatascraped[[2]],
                                     which(examplelist2 == TRUE),
                                     paste(formularydatascraped[[2]][c(which(examplelist2 == TRUE))],       formularydatascraped[[2]][c(which(examplelist2 == TRUE)+1)]))

formularydatascraped[[2]] <- formularydatascraped[[2]][-c(which(examplelist2 == TRUE)+1,
                             which(examplelist2 == TRUE)+2)]

examplelist3 <- formularydatascraped[[2]] %>%
  lapply(function(x) {str_detect(x, pattern = '[0-9][0-9].[0-9][0-9]')})

index <- which(examplelist3 == TRUE)

formularydatascraped[[2]] <- lapply(1:length(index), function(x) {
    if (x+1 <= length(index)) {end <- x+1} else {end <- length(index)}
    formularydatascraped[[2]][index[x]:(index[end]-1)]})

formularydatascraped[[4]] <- lapply(formularydatascraped[[2]], `[[`, 1) #first element in list

formularydatascraped[[5]] <- link %>% # all the titles
    html_nodes(css = ".RowZ100 td , .RowA100 td") %>%
    html_text()

a <- formularydatascraped[[5]][seq(1, length(formularydatascraped[[5]]), 3)]
b <- formularydatascraped[[5]][seq(2, length(formularydatascraped[[5]]), 3)] %>%
     as.character() %>%
     stringr::str_replace_all("\r\n\t  ", replacement = "") %>%
     stringr::str_replace_all("\r\n\ ", replacement = "") %>%
     str_trim()

formularydatascraped[[5]] <- data.frame(a, b) %>% #break down by grouping?
  mutate(second = substr(a, 4, 5),
         third = substr(a, 7, 8),
         fourth = substr(a, 10, 12),
         b = as.character(b))

rm(a,b, examplelist2, examplelist3, index)
```

There are `r length(formularydatascraped[[1]])` antibiotics listed in NHS Tayside formulary.

```{r}
# #get links list
# #get non-formulary list
##work out non-formulary stuff
##does this work?
".boldDrug "
# length(formularydatascraped[[1]])
# Eurgh, I could count the childnodes between comment tags in HTML. That might take a while to write.
```

16`r ##length(formularydatascraped[[1]])` of these are non-formulary. 

```{r}
example <- tibble(All = formularydatascraped[[2]], Breakdown = formularydatascraped[[5]]) %>%
  mutate(All = lapply(All, function(x) {x[-1]})) %>% #remove title from first element of vector.
  mutate(value = lapply(All, function(x) {runif(n=length(x), min=0, max=100) %>% round })) #create values

firstlevel <- example$Breakdown$a %>%
  as.character %>%
  str_trim %>%
  nchar %>%
  as.factor

example2 <- example[which(firstlevel == 11),] %>% #third level items
  dplyr::rename(name = All)  %>% 
  transmute(Breakdown, 
            children = map2(name, value, function(name, value) {data.frame(name, value)}))

example3 <- example[which(firstlevel == 8) ,] %>% #second level items
  mutate(children = NA)

example3[which(firstlevel == 11),]$children <- example2$children

example4 <- example[which(firstlevel == 5),] %>%
  mutate(children = NA) 

example$Breakdown$second[example$Breakdown$second == "01"] <- example4$Breakdown$b[1]
example$Breakdown$second[example$Breakdown$second == "02"] <- example4$Breakdown$b[2]
example$Breakdown$second[example$Breakdown$second == "03"] <- example4$Breakdown$b[3]
example$Breakdown$second[example$Breakdown$second == "04"] <- example4$Breakdown$b[4]
example$Breakdown$second[example$Breakdown$second == "05"] <- example4$Breakdown$b[5]

example5 <- example[which(firstlevel == 8),]

rm(firstlevel)
```

#### Reformating the data

```{r}
Formulary %>%
  select(-V4) %>%
  mutate(value = map(V3, function(x) if (x != "") {runif(1, min=0, max=100) %>% round} else {NA}) %>% as.integer) %>%
  rename(name = V3) %>%
  nest(children = name:value) %>%
  mutate_at("children", function(x) {lapply(x, as.data.frame)}) %>%
  rename(name = V2) %>%
  nest(children = name:children) %>%
  mutate_at("children", function(x) {lapply(x, as.data.frame)}) %>%
  rename(name = V1) %>%
  as.data.frame %>%
  list("name" = "Antimicrobials", "children" = .) -> myjson

myjson %>%
  jsonlite::toJSON() %>%
  write(file="Formulary.json")
```

Try to include V4
```{r}
#formulary either V3 or V4. Separate into two, then recombine and nest together
a <- Formulary %>%
  filter(V4 != "") %>%
  mutate(value = map(V4, function(x) if (x != "") {runif(1, min=0, max=100) %>% round} else {NA}) %>% as.integer) %>%
  rename(name = V4) %>%
  nest(children = name:value) %>%
  mutate_at("children", function(x) {lapply(x, as.data.frame)}) %>%
  rename(name = V3) %>%
  nest(children = name:children) %>%
  mutate_at("children", function(x) {lapply(x, as.data.frame)})

b <- Formulary %>%
  filter(V4 == "") %>%
  select(-V4) %>%
  mutate(value = map(V3, function(x) if (x != "") {runif(1, min=0, max=100) %>% round} else {NA}) %>% as.integer) %>%
  rename(name = V3) %>%
  nest(children = name:value) %>%
  mutate_at("children", function(x) {lapply(x, as.data.frame)})

rbind(a,b) %>%
  rename(name = V2) %>%
  nest(children = name:children) %>%
  mutate_at("children", function(x) {lapply(x, as.data.frame)}) %>%
  rename(name = V1) %>%
  as.data.frame %>%
  list("name" = "Antimicrobials", "children" = .) -> myjson2

myjson2 %>%
  jsonlite::toJSON() %>%
  write(file="Formulary2.json")
rm(a,b)
```

Combining National information:

- [Scottish Medicines Consortium](https://www.scottishmedicines.org.uk)
- [BNF Interactions](https://bnf.nice.org.uk/drug/)
- [The Scottish Antimicrobial Prescribing Group](https://www.sapg.scot)

To give functions using this new data I'll need to graph it using the [D3 Graph Gallery.](https://www.d3-graph-gallery.com/dendrogram.html)

- [D3 Force](https://github.com/d3/d3-force)
- [Most basic radial dendrogram in d3.js](https://www.d3-graph-gallery.com/graph/dendrogram_radial_basic.html)
- [r2d3](https://rstudio.github.io/r2d3/)
